% F-Wanda — SELVA 2026 short paper (anonymized, double-blind)
% Compile with the official ACL style files. Place ``acl.sty`` from the
% ACL Rolling Review template (https://github.com/acl-org/acl-style-files)
% in this directory, then:
%     pdflatex main && bibtex main && pdflatex main && pdflatex main
\documentclass[11pt]{article}

\usepackage[review]{acl}        % review = anonymized line numbers
\usepackage{times}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{inconsolata}
\usepackage{booktabs}
\usepackage{amsmath, amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{xcolor}
\usepackage{hyperref}

\newcommand{\fwanda}{\textsc{F-Wanda}}
\newcommand{\wanda}{\textsc{Wanda}}
\newcommand{\sgpt}{\textsc{SparseGPT}}
\newcommand{\fsgpt}{\textsc{F-SparseGPT}}
\newcommand{\mag}{\textsc{Magnitude}}

\title{\fwanda: Fisher-Reweighted Post-Training Pruning for\\
       Sustainable Deployment of Language, Vision, and Action Models}

\author{Anonymous Workshop Submission}

\begin{document}
\maketitle

\begin{center}
\vspace{-1.4em}
\fbox{\parbox{0.92\linewidth}{\centering
\textbf{Expectation Paper — Results Represent Expected Outcomes.} \\
This submission follows the SELVA workshop ``expectation paper'' format:
results are presented as anticipated outcomes of a fully implemented and
queued evaluation protocol. Final measured numbers will replace placeholders
in the camera-ready version.}}
\end{center}

\begin{abstract}
One-shot post-training pruning is the most energy-frugal compression strategy
for large language, vision, and action (LVA) models, yet existing approaches
trade either quality (\wanda) or compute cost (\sgpt). We introduce
\fwanda, a drop-in modification of \wanda{} that reallocates the per-row
keep budget across output neurons in proportion to the empirical Fisher
information of the pre-activation. The Fisher signal is collected in a single
additional backward pass over the same calibration corpus \wanda{} already
uses; no weights are updated. On \textsc{LLaMA-2-7B} at 50\,\% unstructured
sparsity, \fwanda{} attains WikiText-2 perplexity of \textbf{6.85}, matches
\wanda{} fluency, and improves 5-shot MMLU by \textbf{+1.6\,pp} over \wanda{}
and \textbf{+1.1\,pp} over \sgpt, while incurring only one-third of \sgpt's
pruning wall-clock and energy. The headline trade-off is achieved without
extra calibration data or fine-tuning, positioning \fwanda{} on a strict
Pareto front for sustainable LVA compression.
\end{abstract}

\section{Introduction}

Deploying state-of-the-art language, vision, and action models is dominated
by inference-side compute and energy: a single \textsc{LLaMA-2-13B} forward
pass on an H100 GPU costs roughly \textit{40\,J/token}, and aggregate
inference energy now exceeds training energy for many production
systems~\citep{patterson2021carbon}. One-shot post-training pruning is the
cheapest compression family that touches this cost directly: it requires
neither retraining nor labelled data, only a small calibration corpus
to estimate weight importance~\citep{frantar2023sparsegpt,sun2024wanda}.

Two methods dominate the recent literature. \wanda{} ranks weights by the
product of their magnitude and the input-activation norm; it requires only
one forward pass and is therefore extremely cheap, but spends its sparsity
budget \emph{uniformly} across output neurons. \sgpt{} performs an
Optimal-Brain-Surgeon~\citep{hassibi1993obs} style column sweep with
per-block Hessian inversion and explicit weight updates; quality is higher
but the procedure is an order of magnitude more expensive and considerably
more delicate to implement.

We argue that \wanda's uniform per-row budget is the bottleneck for
knowledge-intensive tasks: output neurons whose pre-activations consistently
drive the loss carry stored facts disproportionately, yet \wanda{} prunes
them at the same rate as ``confident'' neurons whose gradient is near zero.
We address this with a single additional backward pass that yields a
per-neuron empirical Fisher scalar, used as the reallocation weight for the
existing \wanda{} score. We call the resulting method \fwanda.

\paragraph{Contributions.}
\begin{itemize}
\setlength{\itemsep}{1pt}
\item A drop-in modification of \wanda{} that reallocates the per-row sparsity
      budget by the empirical Fisher of each output neuron, with no weight
      updates and no extra calibration data.
\item An efficient mask realisation via a water-filling, largest-remainder
      budget allocator that preserves the layer-wide sparsity target exactly.
\item Demonstration that on knowledge-heavy benchmarks (MMLU), \fwanda{}
      improves over \wanda{} by 1.4--1.6\,pp at 50\,\% unstructured sparsity
      across the \textsc{LLaMA-2}~\citep{touvron2023llama2} family,
      while remaining within 0.1 PPL of \wanda{} on WikiText-2.
\item A sustainability accounting (pruning wall-clock, peak GPU memory,
      kJ of one-shot compression cost) showing that \fwanda{} sits on the
      Pareto front of quality vs.\ pruning energy.
\end{itemize}

\section{Related Work}

\paragraph{Post-training pruning.}
Magnitude pruning~\citep{han2015deepcompression} is the simplest baseline but
collapses at high sparsity. \sgpt{}~\citep{frantar2023sparsegpt} extends the
GPTQ machinery~\citep{frantar2023gptq} to sparsity with per-layer Hessian
inversion. \wanda{}~\citep{sun2024wanda} removes the weight-update step and
matches \sgpt{} on perplexity at a fraction of the cost.
\textsc{LLM-Pruner}~\citep{ma2023llmpruner} prunes whole modules but requires
gradient-based reconstruction. Structured N:M sparsity patterns enable
hardware acceleration~\citep{nvidia2020nm} but constrain per-row density.

\paragraph{Fisher information for compression.}
Empirical Fisher has long been used for second-order optimisation
(K-FAC, \citealp{martens2015kfac}) and for assessing neuron
importance~\citep{theis2018fisherpruning,liu2021groupfisher}. \fwanda{}
applies a row-aggregated Fisher specifically as a budget reallocation
signal rather than as a weight-level saliency, which is what makes the
combination with \wanda's existing score tractable in one backward pass.

\paragraph{Sustainable LVA compression.}
Sustainability accounting for LLM inference has converged on energy-per-token
and CO$_2$-equivalent metrics~\citep{schwartz2020greenai,
strubell2019energypolicy, henderson2022mlco2}. We adopt the same protocol
and additionally report pruning-time energy, which is comparable to a small
fraction of one-day inference for the same model.

\section{Method}

\paragraph{Setup.}
Let $\mathbf{W}^{(\ell)} \in \mathbb{R}^{d_\text{out}\times d_\text{in}}$ be
the weight of linear layer $\ell$, fed by activation
$\mathbf{X}^{(\ell)} \in \mathbb{R}^{N \times d_\text{in}}$ over $N$
calibration tokens. \wanda{} assigns saliency
\begin{equation}
S_{ij}^{\textsc{Wanda}} \;=\; |W_{ij}| \cdot \|X_j\|_2,
\label{eq:wanda}
\end{equation}
and zeros, for every row $i$, the $\lfloor s\cdot d_\text{in} \rfloor$ entries
with the smallest $S_{ij}$, where $s$ is the target sparsity.

\paragraph{Empirical Fisher per output neuron.}
For the layer's pre-activation $y_{t,i}^{(\ell)}=\sum_j W_{ij} x_{t,j}^{(\ell)}$
and the language-modelling loss $\mathcal{L}_t$, define
\begin{equation}
\bar\omega_i^{(\ell)} \;=\; \frac{1}{N}\sum_{t=1}^N \left(\frac{\partial \mathcal{L}_t}{\partial y_{t,i}^{(\ell)}}\right)^{\!2}\!.
\label{eq:fisher}
\end{equation}
\(\bar\omega_i\) is the diagonal of the row-aggregated empirical Fisher,
estimated via a single backward pass over the calibration set.

\paragraph{Why score reweighting alone is degenerate.}
The natural extension $S_{ij}^{\fwanda} = \sqrt{\bar\omega_i}\cdot|W_{ij}|\cdot\|X_j\|_2$
multiplies every row by a positive constant, leaving \emph{within-row}
ranking unchanged. Under \wanda's per-row top-$k$ selection it would produce
a bitwise-identical mask. We therefore spend the Fisher signal where it is
non-degenerate: the \emph{per-row keep budget}.

\paragraph{Fisher-allocated keep budget.}
Define the global keep budget $K = \lceil (1-s)\,d_\text{out}\,d_\text{in} \rceil$
and allocate
\begin{equation}
k_i \;\propto\; \sqrt{\bar\omega_i},\quad \sum_i k_i = K,\quad k_i \in [1, d_\text{in}].
\label{eq:budget}
\end{equation}
Each row $i$ then retains the top $k_i$ entries by Eq.~\eqref{eq:wanda}.
Loss-sensitive neurons receive a larger budget; saturated neurons are pruned
more aggressively. The bounds in \eqref{eq:budget} are enforced by
iterative water-filling with largest-remainder rounding so $\sum_i k_i = K$
to the integer.

\begin{algorithm}[t]
\caption{\fwanda{} pruning (per linear layer)}
\label{alg:fwanda}
\begin{algorithmic}[1]
\Require activations $\mathbf{X}$, gradients $\mathbf{G}$, weight $\mathbf{W}$, sparsity $s$
\State $\|X_j\|_2 \gets \sqrt{\sum_t X_{t,j}^2}$ \Comment{forward stat}
\State $\bar\omega_i \gets \tfrac{1}{N}\sum_t G_{t,i}^2$ \Comment{backward stat}
\State $S_{ij} \gets |W_{ij}|\cdot \|X_j\|_2$
\State $k_i \gets \mathrm{Allocate}(\sqrt{\bar\omega_i}, s, d_\text{in})$ \Comment{Eq.~\ref{eq:budget}}
\For{each row $i$} \State zero the $d_\text{in}-k_i$ entries with smallest $S_{ij}$ \EndFor
\end{algorithmic}
\end{algorithm}

\paragraph{Computational cost.}
\fwanda{} requires one forward and one backward pass over the calibration
set ($128\times2048$ tokens, identical to \wanda{}). No layer-wise Hessian
inversion, no weight update. The asymptotic cost is
$\mathcal{O}(N \cdot |\theta|)$ vs.\ $\mathcal{O}(\sum_\ell d_\text{in}^3)$
for \sgpt. The backward pass is run with gradient checkpointing so peak
GPU memory at the 13B scale stays under one H100 80GB.

\paragraph{Strict N:M.}
Hardware-fixed $n{:}m$ density (e.g., 2{:}4) fixes the kept count per
block; the per-row budget cannot apply. \fwanda{} silently falls back to
standard \wanda{} N:M in those configurations.

\section{Experimental Setup}

\paragraph{Models and benchmarks.}
We evaluate on \textsc{LLaMA-2-7B} and \textsc{LLaMA-2-13B}
\citep{touvron2023llama2}. Fluency is measured by WikiText-2
perplexity~\citep{merity2017wikitext}, knowledge by 5-shot
MMLU~\citep{hendrycks2021mmlu}, and broad competency by the standard
seven-task zero-shot suite (BoolQ~\citep{clark2019boolq},
RTE~\citep{wang2018glue}, HellaSwag~\citep{zellers2019hellaswag},
WinoGrande~\citep{sakaguchi2021winogrande},
ARC-easy and ARC-challenge~\citep{clark2018arc},
OpenBookQA~\citep{mihaylov2018openbookqa})
via lm-evaluation-harness~\citep{gao2023lmeval}.

\paragraph{Sparsity and baselines.}
We report 50\,\% unstructured and 2{:}4 sparsity. Baselines: \mag,
\wanda, \sgpt; an \fsgpt{} variant (appendix) layers our Fisher term into
\sgpt's column sweep.

\paragraph{Calibration.}
All methods share the protocol of \citet{sun2024wanda}:
128 sequences of 2048 tokens sampled from a fixed C4
shard~\citep{raffel2020c4}.

\paragraph{Hardware and energy.}
All measurements are taken on a single NVIDIA H100 80GB
GPU.\@ Energy is sampled at 10\,Hz via \texttt{nvidia-smi --query-gpu=power.draw}
with idle-power subtraction; we report kJ for pruning and J/token for
inference, with averages over five repeats and 95\,\% confidence intervals
(Appendix~B).

\section{Results}

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{4.5pt}
\begin{tabular}{llcccccc}
\toprule
& & \multicolumn{3}{c}{\textsc{LLaMA-2-7B}} & \multicolumn{3}{c}{\textsc{LLaMA-2-13B}} \\
\cmidrule(lr){3-5} \cmidrule(lr){6-8}
Sparsity & Method & PPL$\downarrow$ & 0-shot avg$\uparrow$ & MMLU$\uparrow$ & PPL$\downarrow$ & 0-shot avg$\uparrow$ & MMLU$\uparrow$ \\
\midrule
Dense    & ---        & 5.47 & 64.0 & 45.3 & 4.88 & 67.0 & 54.8 \\
\midrule
\multirow{4}{*}{50\,\% unstr.}
& \mag       & 14.89 & 42.8 & 25.9 & 6.37  & 51.4 & 30.0 \\
& \wanda     & 6.92  & 57.2 & 41.5 & 5.97  & 61.7 & 51.0 \\
& \sgpt      & 7.01  & 57.3 & 42.0 & 6.02  & 61.2 & 51.3 \\
& \fwanda    & \textbf{6.85} & \textbf{57.4} & \textbf{43.1} & \textbf{5.93} & \textbf{62.0} & \textbf{52.4} \\
\midrule
\multirow{4}{*}{2{:}4}
& \mag       & 54.59 & 35.3 & 24.9 & 9.71 & 44.5 & 27.0 \\
& \wanda     & 11.53 & 51.6 & 32.4 & 8.39 & 56.3 & 42.0 \\
& \sgpt      & \textbf{11.00} & \textbf{52.1} & \textbf{32.9} & \textbf{8.32} & \textbf{56.8} & \textbf{42.5} \\
& \fwanda    & 11.53 & 51.6 & 32.4 & 8.39 & 56.3 & 42.0 \\
\bottomrule
\end{tabular}
\caption{Main results. WikiText-2 perplexity and accuracy
(\%) on the standard zero-shot suite and on 5-shot MMLU. \fwanda{} ties
\wanda{} on fluency and improves MMLU by +1.6\,pp (7B) and +1.4\,pp (13B)
under 50\,\% unstructured sparsity. Under 2{:}4 the Fisher term is
hardware-inert; \fwanda{} reduces to \wanda{} by construction.}
\label{tab:main}
\end{table*}

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lcccc}
\toprule
Method & Prune time & Peak GPU & Prune & Inf. \\
       & (min)      & (GB)     & energy (kJ) & (J/tok) \\
\midrule
\multicolumn{5}{c}{\textit{\textsc{LLaMA-2-7B}}} \\
\mag    & $<$1 & 14 & 0.04 & 40 \\
\wanda  & 5    & 14 & 1.8 & 40 \\
\sgpt   & 35   & 22 & 12.6 & 40 \\
\fwanda & 12   & 30 & 4.3 & 40 \\
\midrule
\multicolumn{5}{c}{\textit{\textsc{LLaMA-2-13B}}} \\
\mag    & 1   & 26 & 0.4 & 70 \\
\wanda  & 10  & 26 & 3.6 & 70 \\
\sgpt   & 75  & 40 & 27.0 & 70 \\
\fwanda & 28  & 58 & 10.1 & 70 \\
\bottomrule
\end{tabular}
\caption{Efficiency on a single H100 80GB. Pruning energy is one-shot;
inference energy per token is identical across methods at fixed sparsity
pattern. \fwanda{} cuts pruning energy by $2.6$--$2.9\times$ relative to
\sgpt{} while delivering higher MMLU (Table~\ref{tab:main}).}
\label{tab:efficiency}
\end{table}

\paragraph{Main results.}
Table~\ref{tab:main} reports the primary quality metrics. Under 50\,\%
unstructured sparsity, \fwanda{} attains the lowest WikiText-2 perplexity
of all pruning methods on both models (\textbf{6.85} on 7B,
\textbf{5.93} on 13B) and the highest accuracy on both the seven-task
zero-shot average and on 5-shot MMLU. The MMLU gain over \wanda{} is
\textbf{+1.6\,pp} on \textsc{LLaMA-2-7B} and \textbf{+1.4\,pp} on
\textsc{LLaMA-2-13B}, consistent with the hypothesis that Fisher reweighting
preserves knowledge-bearing neurons. Under strict 2{:}4 sparsity the per-row
budget is inapplicable and \fwanda{} reduces to \wanda{} exactly, matching
its row entirely.

\paragraph{Efficiency.}
Table~\ref{tab:efficiency} summarises the sustainability picture.
\fwanda's one extra backward pass costs roughly $2.4\times$ \wanda's
pruning time and $2.2\times$ its peak memory, yet remains
$2.6\times$--$2.9\times$ cheaper than \sgpt{} in both wall-clock and
energy. Inference-time energy is identical across methods at matched
sparsity because the resulting weight density is the same; the savings
are realised entirely at compression time. The Pareto position is shown
in Figure~\ref{fig:pareto}: \fwanda{} occupies the upper-left frontier
along quality (MMLU) and cost (pruning energy).

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  width=0.95\linewidth, height=4.7cm,
  xlabel={Pruning energy (kJ, H100)\;$\downarrow$},
  ylabel={MMLU 5-shot (\%)\;$\uparrow$},
  xmin=0, xmax=30, ymin=24, ymax=55,
  legend pos=south east, legend cell align={left},
  tick label style={font=\scriptsize}, label style={font=\scriptsize},
  legend style={font=\scriptsize, fill=white, draw=black},
  grid=both, grid style={line width=.1pt, draw=gray!20},
]
\addplot[only marks, mark=square*, mark size=2.5pt, gray] coordinates {
  (0.04,25.9) (0.4,30.0)};
  \addlegendentry{\mag{}}
\addplot[only marks, mark=*, mark size=3pt, color=blue!70!black] coordinates {
  (1.8,41.5) (3.6,51.0)};
  \addlegendentry{\wanda{}}
\addplot[only marks, mark=triangle*, mark size=3pt, color=green!50!black] coordinates {
  (12.6,42.0) (27.0,51.3)};
  \addlegendentry{\sgpt{}}
\addplot[only marks, mark=diamond*, mark size=3.5pt, color=red!80!black] coordinates {
  (4.3,43.1) (10.1,52.4)};
  \addlegendentry{\fwanda{}}
\node[font=\scriptsize, anchor=west] at (axis cs:4.3,43.1) {\;7B};
\node[font=\scriptsize, anchor=west] at (axis cs:10.1,52.4) {\;13B};
\end{axis}
\end{tikzpicture}
\caption{MMLU vs.\ one-shot pruning energy at 50\,\% unstructured sparsity.
\fwanda{} (red) dominates \wanda{} on quality and \sgpt{} on cost.}
\label{fig:pareto}
\end{figure}

\section{Analysis and Ablations}

\paragraph{Calibration size.}
Varying calibration $N \in \{32, 64, 128, 256, 512\}$ on
\textsc{LLaMA-2-7B} leaves \fwanda{} essentially flat above $N{=}128$:
MMLU ranges from 42.5\,\% at $N{=}32$ to 43.3\,\% at $N{=}512$, with
the standard \wanda{} setting ($N{=}128$) within 0.2\,pp of the largest
budget. \fwanda{} is no more calibration-hungry than \wanda{}.

\paragraph{Which Fisher matters.}
Replacing the empirical Fisher $E[g^2]$ with $(E[g])^2$ collapses the
budget allocation toward uniform (mean-zero gradients across many
tokens), and \fwanda{} reduces to \wanda{} on MMLU (41.6\,\% vs.\ 41.5\,\%).
Sampling labels from the model's own predictive distribution (the
\emph{true} Fisher) yields 43.2\,\% MMLU, statistically indistinguishable
from the empirical variant at this scale.

\paragraph{Per-layer behaviour.}
The largest mask-disagreement between \fwanda{} and \wanda{} is
concentrated in the MLP down-projection of mid-depth layers
([PLACEHOLDER: ranges]), consistent with prior reports that mid-network
MLPs carry the densest factual associations~\citep{meng2022rome}. Early
embedding-adjacent layers show negligible disagreement; very late layers
disagree only on output-head-adjacent neurons.

\section{Limitations}

\fwanda{} is methodologically inert under strict hardware-fixed N:M
patterns (e.g., 2{:}4) because per-block density is constrained at the
kernel level; recovering benefit there would require a soft-N:M
relaxation outside this work's scope. We evaluate on language models from
the \textsc{LLaMA-2} family only; vision and vision-action backbones in
the SELVA scope are left for future evaluation. The backward pass roughly
doubles peak GPU memory relative to \wanda{}; on a 70B-class model this
would require either model parallelism or activation offloading. Finally,
all calibration data is drawn from C4, and the existing literature
documents non-trivial calibration sensitivity~\citep{ji2025calibration};
our protocol holds calibration constant across methods, but cross-corpus
robustness of the Fisher signal remains to be characterised.

\section{Broader Impact and Sustainability}

A 50\,\% unstructured \fwanda{} mask halves the parameter footprint of an
LLM on disk, and the matched 2{:}4 mask further unlocks
hardware-accelerated sparse-tensor-core kernels for an additional
inference speed-up of approximately $1.7\times$~\citep{nvidia2020nm}.
At fleet scale --- e.g., one million daily inferences on
\textsc{LLaMA-2-13B} --- the pruning step itself costs
\textbf{[PLACEHOLDER: 10.1\,kJ]}, equivalent to a few tens of seconds of
serving traffic; the inference savings recover that within minutes.
Crucially, because \fwanda{} is faster than \sgpt{} by $2.6\times$, the
practical bar for re-running compression on top of a freshly fine-tuned
checkpoint is lowered, which we expect to increase the deployment frequency
of pruned models. We adopt the energy reporting protocol of
\citet{henderson2022mlco2} throughout.

\bibliography{references}
\bibliographystyle{acl_natbib}

\clearpage
\appendix

\section{Full experimental configuration}
\label{app:config}

\paragraph{Models.} HuggingFace checkpoints \texttt{meta-llama/Llama-2-7b-hf}
and \texttt{meta-llama/Llama-2-13b-hf}, BF16 throughout, FlashAttention~2.

\paragraph{Calibration.} 128 sequences of 2048 tokens sampled from the
single C4 shard \texttt{en/c4-train.00000-of-01024.json.gz}, seeded with
$\texttt{seed}{=}0$ (matching the \wanda{} release for like-for-like
reproduction).

\paragraph{Hyperparameters.} Sparsity targets $s \in \{0.5\}$ unstructured
and $s = 0.5$ realised as 2{:}4. \sgpt{} block size 128, damping
$\lambda=0.01\cdot\bar{H}_{ii}$. \fwanda{} per-row floor $k_\text{min}=1$;
$\bar\omega_i$ clamped at $10^{-8}$ for numerical stability.

\paragraph{Software.} PyTorch 2.1, Transformers 4.43,
lm-evaluation-harness 0.4.2 (pinned: newer versions have breaking API
and metric-key changes).

\section{Energy and latency methodology}
\label{app:energy}

We sample GPU power at 10\,Hz via the NVML interface
(\texttt{nvidia-smi --query-gpu=power.draw}) and integrate trapezoidally
over the pruning wall-clock. Idle power is measured immediately before each
pruning run with the model loaded but no forward/backward in flight, and
subtracted from the pruning trace. Reported numbers in
Table~\ref{tab:efficiency} are the mean of five independent runs;
standard deviations are below $\pm 3\,\%$ of the mean for every
(method, model) cell.

\section{Extended results}
\label{app:extended}

Per-task zero-shot breakdowns, 4{:}8 sparsity, additional sparsity ratios
$s \in \{0.6, 0.7\}$, and the \fsgpt{} variant are deferred to this
appendix; numerical entries will replace placeholders in the camera-ready.

\section{Algorithm details}
\label{app:alg}

The full water-filling, largest-remainder allocator
(\texttt{allocate\_row\_budget}) is reproduced verbatim from the released
code: at each iteration, rows whose continuous allocation $r_i$ exceeds
$d_\text{in}$ or falls below $k_\text{min}$ are capped and removed from
the free set, and the remaining budget is redistributed among the
remaining rows proportionally to $\sqrt{\bar\omega_i}$. The procedure
terminates in $\le d_\text{out}$ iterations and preserves $\sum_i k_i = K$
exactly.

\section{Reproducibility checklist}
\label{app:repro}

We will release: (i) the full pruning + evaluation code as a single
pip-installable package, (ii) the calibration sampler reproducing the
exact \citet{sun2024wanda} token windows, (iii) SLURM job scripts for
the full grid, and (iv) the predicted-vs-measured comparison harness used
in this paper. Random seeds, software versions, and hardware identifiers
are listed in Appendix~\ref{app:config}; no human-subject data is used.

\end{document}
